Education Analysis of the United States

### 2023-03-17 outputs/paper/paper.qmd
final edit

The remainder of our paper holds four sections. In section 2, we explain the data source and methodology used for data collection, potential bias and ethics issues, and the variables we use. In Section 3, we present our results and the findings. Finally, in Section 4, we discuss what the results we found mean, weaknesses and limitations in our paper, and the next steps we can take to enhance the findings of this report.

>>>>

The remainder of our paper holds four sections. In section 2, we explain the data source and methodology used for data collection, potential bias and ethics issues, and the variables we use. In Section 3, we present our results and the findings and discuss what the results mean in Section 4. Finally, in Section 5 we go over the weaknesses and limitations in our paper, and the next steps we can take to enhance the findings of this report.
